Most of tha ghettos currently accessible hydrocarbon resources is found up in tight rocks - rocks wit permeabilitizzles up in tha millidarcy range n' wit pore sizes up in tha nanometer range. Tight rocks pose freshly smoked up scientistical problems cuz of tha lil' small-ass length-scalez involved. Y'all KNOW dat shit, muthafucka! Traditionizzle oil skits is found in, fo' example, sand stone reservoirs wit millimeter ta micrometer sized pores. For such systems, standard hydrodynamics be a sufficient tool ta understand, describe n' predict fluid transport. In tight rocks, however, typical pore sizes is up in tha range of tens ta hundredz of nanometas fo' realz. At dis scale, tha mean free path - tha average distizzle a particle moves between collisions - may become comparable ta tha characteristic sizez of tha porous medium, n' tha standard assumption dat tha fluid can be busted lyrics bout as a cold-ass lil continuum no longer holds. Da mean free path of dilute gases is often tenz of nanometers, or higher n' shit. 

Da gas from tight rocks, like shales, is stored inside closed pore networks or adsorbed onto organic matter n' shit. In order ta extract adequate levelz of gas from such rocks, we generate fractures ta increase tha permeabilitizzle of tha rock. Da gas flows from lil' small-ass pore networks wit diametas down ta all dem nanometers. Da rate at which tha gas flows all up in such networks is proportionizzle ta tha permeabilitizzle of tha material - a result known as Darcyz law. Dilute gases up in nanoporous media gotz a non-zero slip velocitizzle which can cause a increase of permeabilitizzle of a gangbangin' factor 50 compared ta what tha fuck continuum theory predicts, n' you can put dat on yo' toast. This be a effect known as tha Klinkenberg effect. In order ta be able ta increase gas thang rates up in a safe way, we need ta KNOW tha physics at dis scale. This requires models dat is valid at these length scales.

In dis thesis, we implement two numerical particle models. Da first is called Molecular Dynamics. Well shiiiit, it raps bout tha motion of atoms by rockin parameterized potentials ta compute forces between em. Da second model, Direct Simulation Monte Carlo, uses tha principlez of statistical mechanics allowin larger systems ta be studied. Y'all KNOW dat shit, muthafucka! Both implementations support arbitrary geometries, n' show promisin scalin efficiency on massive parallel machines. We use these models ta study tha Klinkenberg effect n' confirm dat tha Knudsen permeabilitizzle erection erectly predicts tha permeabilitizzle fo' systems wit pore sizes down ta all dem nanometers. We also analyze mo' fucked up geometries, n' argue dat a stochastic version of tha Knudsen erection is needed fo' geometries without a well defined Knudsen number n' shit. 

Highly efficient custom 3D visualization tools is pimped rockin modern OpenGL steez like fuckin instanced geometry shaders, billboardz n' tha marchin cubes algorithm. Right back up in yo muthafuckin ass. Systems wit tenz of millionz of particlez can be rendered realtime wit decent frame rate, allowin our asses ta study larger systems than what tha fuck can be done wit already existin free software fo' realz. All software pimped durin dis thesis can serve as tools fo' further study up in tha field.