My fuckin first encounter wit physics was up in high school wit mah physics mackdaddy Knut L{\o}vseth. I remember yo' classes. They was filled wit enthusiazzle n' joy - you flossed how tha fuck much you ludd physics n' science. Yo ass be a legit inspirer, a pimped out motivator. Shiiit, dis aint no joke. I be grateful fo' how tha fuck you flossed mah crazy ass tha path ta what tha fuck I gots a straight-up boner fo' da most thugged-out - physics.

Later on, all up in tha university, when I attended lectures up in tha introductory course up in mechanics, I kicked it wit Pimp Andaz Malthe-S{\o}renssen, whoz ass later became mah supervisor. Shiiit, dis aint no joke. I wanna fuck you fo' bein another straight-up inspirin person. I aint talkin' bout chicken n' gravy biatch. Every time we rap I git motivated n' horny fo' peepin' more, explorin freshly smoked up scams n' connectin tha dots up in mah game. I trip off every last muthafuckin rap bout physics, startups n' chizzlez up in tha game up in general. It aint nuthin but tha nick nack patty wack, I still gots tha bigger sack. 

I would also like ta give props ta Svenn-Arne Dragly, whom I have shared endless minutes with, havin funk peepin' OpenGL, programming, physics n' useless thangs like stories bout prisoners n' chests, n' you can put dat on yo' toast. Our work together do not stop here, we will continue bustin dunkadelic stuff.

Learnin bout Molecular Dynamics n' statistical mechanics has been a joyful ride props ta Kjetil Th{\o}gersen, J{\o}rgen Kjoshagen Tr{\o}mborg n' Camilla Kirkemo Alm fo' realz. All our raps bout potentials, water, salt, no salt, erroneously salt n' cage correlation functions done been pimped out fo' realz. Also, fuck you fo' all yo' help wit mah thesis. I look forward ta hustlin wit you over tha next years.

A big-ass props ta mah playas all up in tha Computationizzle Physics group. Yo ass make me look forward ta work tha next morning, dizzle afta day, week afta week fo' realz. And of course, a special props ta Andreas Nakkerud. Y'all KNOW dat shit, muthafucka! All tha weird thangs our crazy asses have done tha past muthafuckin years done been pimped out. Lastly, I wanna give props ta Thea Marcelia Sletten. I aint talkin' bout chicken n' gravy biatch. Yo ass be a dunkadelic person.

\raggedleft Oslo, 30 March, 2014\\
\raggedleft Anders Hafreager