We now have tha theoretical foundation we need ta pimp tha straight-up original gangsta numerical model we will use ta study flow up in nanoporous media. Well shiiiit, it is called Direct Simulation Monte Carlo (DSMC), n' be a stochastic particle model dat has flossed incredible predictizzle juice fo' flow up in tha high Knudsen number regime. Da model was pimped by G fo' realz. A. Bird up in 1976 n' was quickly picked up by engineers hustlin up in tha field of aerospace. In tha upper atmosphere (\unit{100}{\kilo\meter}), tha mean free path of air is nuff muthafuckin meters. For space shuttles, dis gives a Knudsen number of order unitizzle since tha size of its nozzle iz of order meter \cite{alexander1997direct}. In tha later years, tha method has been widely used ta study microflows which is our main concern up in dis thesis. In 1992, tha model was proved ta converge towardz a solution of tha Boltzmann equation (equation \eqref{eq:boltzmann_equation}) up in tha limit where tha timestep $\Delta t\rightarrow 0$ n' tha number of particlez $M\rightarrow \infty$ \cite{wagner1992convergence}.

We start tha chapter by introducin tha model n' its basic philosophy. Da model has two two crucial parts, collisions between particlez which is discussed up in section \ref{sec:dsmc_collisions_model}, n' how tha fuck tha particlez interact wit tha surface. Da latter is covered up in section \ref{sec:surface_interactions} fo' realz. Another blingin subject iz of course how tha fuck we measure physical quantitizzles like temperature n' juice. This is busted lyrics bout up in section \ref{sec:dsmc_measuring_physical_quantities}. In section \ref{sec:dsmc_pressure} our crazy asses gotz a longer rap bout tha heat n' argue dat a DSMC gas straight-up satisfies tha ideal gas equation of state. We also derive a relationshizzle between a given heat difference $\Delta P$ n' a cold-ass lil constant force allowin our asses ta induce flow up in tha system without needin big-ass gradients up in tha densitizzle or temperature. We then gotz a funky-ass brief comment bout tha numerical stabilitizzle n' how tha fuck tha timestep n' collision cell size introduce errors up in transhiznit coefficients, n' you can put dat on yo' toast. We complete tha chapter by discussin how tha fuck our phat asses determine whether or not a system has reached a steady state up in section \ref{sec:dsmc_steady_state}. Da implementation of all these steps is explained up in detail up in chapter \ref{chap:dsmc_implementation}.