\section{Rap}
Our thugged-out asses have used two fundamentally different models ta study flow up in similar systems. MD be a atomic model computin forces between every last muthafuckin atom whereas DSMC be a stochastic particle model based on statistical mechanics. Right back up in yo muthafuckin ass. Studyin a physical problem dis way has a pimped out strength; when two models wit different assumptions smoke on tha thangs up in dis biatch, our crazy asses have, ta a pimped outer extent, reasons ta trust dem than if dat shiznit was just one model. But up in any model, we make assumptions, n' these may produce wack lyrics. Da main reason ta use DSMC rather than MD iz of course tha reduced computationizzle cost. This points up a blingin fact; tha mo' physics you include up in a model, tha mo' computationizzle high-rollin' it is. This leadz ta tha fundamenstrual problem we always hook up before choosin a model; what tha fuck is tha physical problem, n' what tha fuck is tha relevant phenomena?

A complete model of shale gas extraction should include physics describin both tha gas thang up in tha nanometer pores as well as tha big-ass scale flow from tha fractures tha fuck into tha drillin hole. Todizzle our phat asses aint gots any phat models coverin dis big-ass range up in length scalez n' time scales. On tha larger scale, we use continuum mechanics whereas tha smalla scale requires models like MD or DSMC. On tha smallest scale there be nuff muthafuckin alternatives ta these two. Other ghettofab methodz is tha lattice Boltzmann (LB), dissipatizzle particle dynamics (DPD), which both can simulate larger systems fo' lager times. But again, a gangbangin' fasta model probably includes less physics fo' realz. A comparison between DSMC n' these models would be interesting.

Both models our crazy asses have studied have indeed shown promisin thangs up in dis biatch, calculatin permeabilitizzles up in nanopores up in agreement wit tha Knudsen erection yo, but there might be other blingin effects we aint included up in tha models. Right back up in yo muthafuckin ass. Such effects is probably not incorporated up in tha Knudsen erection either yo, but could become evident up in a experiment. Validation of a model aint necessarily a validation of tha assumptions. For example, if tha surfaces inside tha pores gotz a non-zero net charge, it could hella affect tha fluid flow n' tha permeability. We can incorporate dis up in MD by rockin a mo' advanced potential. It aint nuthin but tha nick nack patty wack, I still gots tha bigger sack. Da model we used ta create a solid up in MD used a harmonic oscillator potential ta keep tha atoms at approximately tha same posizzle as they started, keepin tha geometrical form of tha solid. Y'all KNOW dat shit, muthafucka! While dis model includes realistic atomic forces n' vibrations inside tha solid, deformations n' fracturin is now impossible since tha atoms is forced up in tha original gangsta formation.

It be also assumed dat tha gas is trapped both inside already existin pores as well as adsorbed onto tha organic material inside tha shales. Da rate of desorption from tha organic material may require additionizzle models releasin tha gas from tha organic material ta tha fracture network. These is just a gangbangin' few yo, but blingin remarks bout tha limitationz of tha models. Well shiiiit, it is needless ta say dat they is not complete up in any sense. Even if they \textit{were} complete, if they calculated both gas thang n' flow from tha smallest pores tha fuck into tha fracture network, we would not be even close ta a cold-ass lil complete model of a shale reservoir. Shiiit, dis aint no joke. Da couplin between different length scalez - multi scale physics - is still a unsolved problem up in physical science.

From tha theoretical perspective, we used tha Knudsen erection ta predict permeabilitizzles up in geometries wit a cold-ass lil closed form solution fo' tha absolute permeabilitizzle all up in tha no-slip scale. If we work wit a geometry without a known absolute permeability, we can measure dis up in tha high densitizzle limit, n' still use tha Knudsen erection ta predict permeabilitizzles fo' dilute gases. Da erection factor be a gangbangin' function of tha Knudsen number, which be a well defined quantitizzle up in simple geometries like a cold-ass lil cylinder n' shit. But fuck dat shiznit yo, tha word on tha street is dat fo' mo' fucked up geometries like tha packed spheres, tha Knudsen number should rather be peeped as a gangbangin' finger-lickin' distribution than one single number n' shit. Well shiiiit, it is possible, as our phat asses say shit bout up in appendix \ref{app:knudsen_number_packed_spheres}, ta calculate a gangbangin' finger-lickin' distribution of Knudsen numbers providin both tha mean value n' tha standard deviation which may be used ta pimp a \textit{stochastic} Knudsen erection based on tha original gangsta model. By obtainin statistical shiznit bout tha geometry of a real shale reservoir, such a theory could up in principle enable our asses ta do a economical risk analysis based on tha permeabilitizzle distribution. I aint talkin' bout chicken n' gravy biatch. 