\section{Future work}
No matter how tha fuck much work our phat asses do, freshly smoked up scams pop our mindz fasta than we manage ta complete tha oldschool ones. Durin tha past months, all up in every last muthafuckin thang our crazy asses have hustled, both scams bout extensions ta tha models n' applications have emerged. Y'all KNOW dat shit, muthafucka! First of all, as our phat asses discussed up in section \ref{sec:dsmc_steady_state}, our analysiz of whether or not tha system has reached a steady state is inadequate. New, automatic methodz should be incorporated by, up in nuff muthafuckin regions (for example by rockin tha collision cells up in DSMC), lookin at expectation joints n' tha variizzle of physical quantitizzles like fuckin momentum, juice n' temperature. Even wit a mo' advanced analysiz of if tha steady state is reached or not, reachin a steady state may take a long-ass time. In tha benchmark we performed n' discussed up in section \ref{sec:dsmc_parallelization_performance}, 512 processors used 545 secondz ta proceed 500 timesteps wit one bazillion particles. If tha system requires 100k timesteps ta reach a steady state, dis would require 15k cpu minutes just ta reach tha steady state. With DSMC, it may be possible ta bust a smalla number of particlez (that is, increase tha number of effectizzle atoms per simulated particle) while tha system reaches a steady state. Then, before tha sampling, increase tha total number of particlez by distributin a fuckin shitload of particlez wit tha velocitizzles n' densitizzles computed from tha previous simulation, equilibratin dis state before startin tha sampling.

A detailed study of how tha fuck tha Cercignani-Lampis collision model from section \ref{sec:surface_interactions} affects tha permeabilitizzle would also be a bangin-ass n' blingin work yo. Here one could fo' example also use tha Lennard-Jones MD model ta fire single atoms towardz a surface n' gather a gangbangin' finger-lickin' distribution ta compare wit tha Cercignani-Lampis model.

With tha voxelization model of tha surface our phat asses pimped up in section \ref{sec:dsmc_complex_geometries} all dem thangs quickly arise. What is tha effectz of tha discretization of tha geometry, biatch? A real, smooth surface do indeed look different than a jagged surface composed by voxels. With dis representation, tha effectizzle surface area is increased which could affect tha flow fo' realz. A detailed study of these effects should be carried out. Right back up in yo muthafuckin ass. Such a representation also requires a shitload of memory as tha memory requirement scalez as $O(N^3)$. To save memory, we can bust a sparse voxel octree representation. I aint talkin' bout chicken n' gravy biatch. If a larger crew of voxels all share tha same value, only one, larger voxel is saved up in memory, representin all tha smalla voxels.

Since tha matrix already is on a gangbangin' finger-lickin' discretized grid n' tha net momentum transfer from tha particlez is calculated durin collisions, it is possible ta extend tha model ta include deformation n' crackin which is blingin processes inside tha shales. Production from organic material can also be included by includin a gangbangin' finger-lickin' diffusion solver on tha matrix dat can desorb n' adsorb gas particles.

For a big-ass number of processors, tha amount of work each processor be assigned may not be equal ta all tha others. This means dat a processor dat is computin only half tha work than another processor, it will spend 50$\%$ of its time waitin fo' tha other processors ta finish. Da solution ta dis is known as load balancin fo' realz. An analysiz of tha system prior ta tha simulation may distribute tha amount of work not by dividin tha system tha fuck into equal \textit{total volumes} yo, but equal \textit{pore volumes} up in which tha particlez are. Da amount of work is proportionizzle ta tha number of particlez a processor has fo' realz. A last yo, but straight-up bangin-ass task we wanna do is simulate gas all up in a nanoporous media from a real material. It aint nuthin but tha nick nack patty wack, I still gots tha bigger sack. Right back up in yo muthafuckin ass. Such data can be obtained wit a technique called focused ion beam scannin electron microscopy (FIB-SEM). 