Before our phat asses describe tha straight-up original gangsta model, tha Direct Simulation Monte Carlo, we need ta say shit bout some theory. Da model is based on tha kinetic theory of gases, which be a microscopic theory dat raps bout tha behavior of gases all up in tha molecular level fo' realz. A system of $N$ particlez is straight-up busted lyrics bout by tha $3N$ momentum components combined wit tha $3N$ spatial coordinates. Together, dis forms a $6N$ dimensionizzle phase space where each point represents tha state of tha system up in a ensemble. We start dis chapter by introducin tha distribution function, tha conceptz of microstates, macrostates n' ensemblez up in section \ref{sec:kinetic_theory_distribution_function}, before we up in section \ref{sec:kinetic_theory_ensemble_averages} explain how tha fuck we measure tha macroscopic observablez which is average joints over all tha states up in a ensemble. Then our crazy asses gotz a funky-ass brief rap bout ergodicitizzle up in section \ref{sec:kinetic_theory_ergodicity} which be a straight-up blingin assumption when we start measurin physical quantitizzles up in a numerical statistical mechanics model like fuckin Direct Simulation Monte Carlo (chapter \ref{chap:dsmc}) n' Molecular Dynamics (chapter \ref{chap:md}). In section \ref{sec:boltzmann_equation} our phat asses derive tha Boltzmann equation which is tha fundamenstrual equation dat governs tha behavior of tha distribution function. I aint talkin' bout chicken n' gravy biatch. We then define what tha fuck a equilibrium state is which we use ta derive tha Maxwell-Boltzmann velocitizzle distribution up in section \ref{sec:maxwell_boltzmann_distribution} fo' realz. As we might remember, tha Knudsen number be a blingin dimensionless quantitizzle dat we use ta quantify how tha fuck blingin surface n' non-continuum effects are. Da Knudsen number is tha ratio between tha mean free path $\lambda$ n' some characteristic length $L$ of tha system. In section \ref{sec:mean_free_path_calculation} we calculate tha mean free path which is used ta compute tha mean collision time $\tau_\text{coll}$, which is blingin ta chizzle a phat timestep up in tha Direct Simulation Monte Carlo model up in chapter \ref{chap:dsmc}.
\section{Da distribution function}
\label{sec:kinetic_theory_distribution_function}
A point $(\vec r, \vec v)$ up in tha phase space raps bout what tha fuck is called a \textit{microstate} n' gotz nuff a massive amount of shiznit. I aint talkin' bout chicken n' gravy biatch. Given dis point, we would know tha posizzle n' velocitizzle ta \textit{every} particle up in tha entire system. In a liter of a ideal gas under standard pressure, tha number of particlez iz of order $10^{22}$ \cite{garcia2000numerical}, so if each of these $6N$ coordinates was represented as a 8 byte \textit{double} on a cold-ass lil computer, we would need mo' than $10^{11}$ terabytez of memory just ta store all tha shiznit. I aint talkin' bout chicken n' gravy biatch. This approach would be straight-up inconvenient and, fortunately, not at all necessary. Da straight-up bangin-ass propertizzles up in a system is tha macroscopic ones, like juice, temperature, pressure, volume, average velocitizzle among others. For example, tha total juice up in a gas consistin of $N$ particlez is calculated as
\begin{align*}
	E = \sum_{i=1}^N \frac{1}{2} m_i v_i^2 + V(\vec r),
\end{align*}
where $m_i$ is tha mass of particle $i$, $v_i$ is its scalar velocitizzle n' $V(\vec r)$ is tha total potential juice up in tha system dependin on tha full $3N$-dimensionizzle spatial coordinizzle $\vec r$.\\
Given a microstate, what tha fuck happens if we switch two particles, say particle $i$ n' $j$, biatch? If particle $i$ had velocitizzle $\vec v_i = \vec u$ n' particle $j$ had some other velocitizzle $\vec v_j = \vec w$, we could quickly swap dem so dat $\vec v_i = \vec w$ n' $\vec v_j = \vec u$ (theoretically of course, it would be a gangbangin' finger-lickin' hard as fuck task up in a experiment). If they masses is identical, tha total juice of tha system would not chizzle yo, but since \textit{we} know dat we switched tha two particles, we could wanna count dis as another microstate. We could up in principle paint tha particlez wit different colors, or maybe just label dem wit they own unique number n' shit. But fuck dat shiznit yo, tha word on tha street is dat up in a real, mono-atomic gas, we can't straight-up tell tha difference if particle $i$ n' $j$ secretly agreed ta switch places without spittin some lyrics ta us. If they did so, it would not count as different microstates, tha system remains exactly tha same. We say dat tha particlez is \textit{indistinguishable}.

If we instead increase tha velocitizzle of particle $i$, we can reduce some another particle $j$z velocitizzle ta keep tha total juice constant. Even though tha macroscopic property \textit{energy} is unchanged, there be a (theoretically) measurable difference between these two states. Da set of all microstates dat share tha same macroscopic state variablez (a \textit{macrostate}) forms a ensemble of systems fo' realz. A much used ensemble is tha microcanonical ensemble (NVE) wit a cold-ass lil constant number of particlez $N$, constant volume $V$ n' constant juice $E$. Increasin tha velocitizzle of particle $i$ while all up in tha same time reducin particle $j$z velocitizzle just enough ta remain tha juice unchanged do not chizzle tha particle number $N$, tha volume $V$ or tha juice. Right back up in yo muthafuckin ass. So these two different microstates would both be up in tha same ensemble.

In a typical system, tha number of microstates up in a macrostate is so big-ass dat tha phase space points can be busted lyrics bout by a cold-ass lil continuous densitizzle function $f(\vec p, \vec r, t)$ without losin any blingin shiznit \cite{mcquarrie1973statistical}. Da input parametas is tha $3N$ momentum components, tha $3N$ spatial coordinates plus time. This function is often called a \textit{distribution function}, normalized so that
\begin{align}
	\iint\! f(\vec p, \vec r, t) \dm \vec p\dm \vec r = N,
\end{align}
where $\dm \vec p\dm \vec r=\dm p_1\dm p_2...\dm r_{3N}$ is tha $6N$ dimensionizzle phase space volume element. This densitizzle function do not contain tha shiznit bout tha \textit{exact} positions or momenta of tha particlez yo, but tha \textit{probability} ta find tha system up in a state round a given phase space point. We can then use it ta calculate measurable, macroscopic average joints, n' you can put dat on yo' toast. 

\section{Ensemble averages}
\label{sec:kinetic_theory_ensemble_averages}
Given tha distribution function $f$, we can calculate any ensemble average (which is ghon be tha measurable, macroscopic propertizzlez of tha system) by interpretin $f$ as a probabilitizzle distribution (it needz tha factor $1/N$ ta be normalized ta one) dat gives tha probabilitizzle of findin a particle at posizzle $\vec r + \dm \vec r$ wit momentum up in tha range $\vec p + \dm\vec p$ all up in tha time $t$. We can then use tha standard expectation value expression ta calculate a macroscopic property $\bar A$
\begin{align}
	\label{eq:ensemble_average}
	\bar A(t) = \frac{1}{ N}\iint\! A(\vec p, \vec r, t)f(\vec p, \vec r, t)\dm \vec p\dm\vec r.
\end{align}
This could fo' example be tha total juice
\begin{align}
	\bar E(t) &= \frac{1}{ N}\iint\! E(\vec p, \vec r, t)f(\vec p, \vec r, t)\dm \vec p\dm\vec r \\
	&= \frac{1}{ N}\iint\! \left(V(\vec r) + \sum_{i=1}^N \frac{\vec p_i^2}{2m_i} \right)f(\vec p, \vec r, t)\dm \vec p \dm \vec r,
\end{align}
where $\vec p_i$ is tha momentum of particle $i$ fo' realz. Any other quantitizzle of interest can up in principle be measured up in tha same way. 

\section{Ergodicity}
\label{sec:kinetic_theory_ergodicity}
Da ensemble average calculates tha average value of some macroscopic quantitizzle given tha distribution function $f$. Usually, our phat asses aint gots tha distribution function, except up in some straight-up simple theoretical calculations. Even then, it might be hard as fuck ta compute tha integral up in equation \eqref{eq:ensemble_average}. Da usual thang when our phat asses do numerical statistical mechanics is dat our crazy asses gotz a way ta explore tha phase space, hopin dat it helps our asses visit states wit probabilitizzles accordin ta tha given ensemble. Many Monte Carlo steez (like fuckin tha Metropolis algorithm) allow our asses ta git all up in a new, random point up in tha phase space, n' calculate tha probabilitizzle of goin from tha current state ta tha freshly smoked up state. From this, we can count tha number of times our crazy asses have hit up different regionz of tha phase space n' create a histogram or maybe, if our slick asses dirty, fit some existin probabilitizzle distribution ta our data.

Another approach is ta let tha rulez of physics take our asses round up in tha phase space, from one state ta another, followin Newtonz equationz of motion. I aint talkin' bout chicken n' gravy biatch. Imagine dat at $t=0$, our system is up in some microscopic state (a single phase space point ($\vec r(0), \vec p(0)$)) n' at a later time $t=\tau$ has moved ta ($\vec r(\tau), \vec p(\tau)$). Between these two points, tha system has moved all up in nuff other points, explorin tha phase space. Well shiiiit, it seems reasonable dat up in tha limit of infinite time, tha time evolution should visit tha phase space points accordin ta tha densitizzle given by $f$. If not, it wouldn't make any sense even rappin' bout $f$, since it is tha time evolution we, as humans, is fuckin wit up in tha real physical ghetto. Right back up in yo muthafuckin ass.

This is called tha ergodicitizzle hypothesis, tha assumption dat a system followin tha lawz of physics, explores tha phase space wit tha probabilitizzle of bein up in a region proportionizzle ta tha densitizzle up in dat region. I aint talkin' bout chicken n' gravy biatch. Da average value of a macroscopic quantitizzle $A$ is then found as
\begin{align}
	\bar A = \lim_{t\rightarrow \infty} \frac{1}{t}\int_0^{t} A(\vec r(t'), \vec p(t'), t')\dm t'.
\end{align}